% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
% !Mode:: "TeX:UTF-8"

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
\usepackage{linespacing_fix} % disable extra space before next section
\usepackage{cite}
\usepackage[colorlinks,linkcolor=blue]{hyperref}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Jianpeng Hou}
\centerline{Machine Learning; Software Development}
\vspace{2ex}
\contactInfo{houjp1992@gmail.com}{(+86) 152-0000-0000}{ \url{https://github.com/houjp/}}

 
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Institute of Computer Technology, Chinese Academy of Sciences}}{Sep. 2014 -- Jul. 2017}
\textit{Master student} in Computer Software \& Theory, Rank: top 5\%
\datedsubsection{\textbf{University of Science \& Technology Beijing}}{Sep. 2010 -- Jul. 2014}
\textit{Bachelor student} in Computer Science \& Technology, Rank: \nth{4}/124

\section{\faUsers\ Project Experience}

\datedsubsection{\textbf{Big Data Analysis Platform (\href{http://159.226.40.104:18080}{http://159.226.40.104:18080})}}{Oct. 2015 -- Mar. 2016}
\begin{itemize}
  \item  Developed distributed algorithms(CART/GBDT/GBRT/RF) on Spark.
  \item Finished data mining components(Feature-Indexing/Feature-Merging/Feature-Normalization/Scoring).
\end{itemize}

\datedsubsection{\textbf{China Telecom Big Data Application Contest (\nth{1}/1112; Team Leader)}}{Dec. 2015 -- Mar. 2016}
The goal of this contest is to predict views of users with ten sites succeeding, according to four hundred million user-behavior historical records(25.38G).
\begin{itemize}
  \item Proposed and implemented a multi-target regression algorithm on Spark. Optimized F1-score 0.8\%.
  \item Designed and developed a probability ranking model for user classification. Optimized F1-score  0.6\%.
\end{itemize}

\datedsubsection{\textbf{SIGHAN-2015 Chinese Spelling Check Task (\nth{1} Place)}}{Mar. 2015 -- May. 2015}
The goal of this task is to detect and correct spelling errors on Chinese essays.
\begin{itemize}
  \item Handled this task with a unified framework which consisted of candidate generating, two stage candidates re-ranking and global decision making.
  \item Finished candidate generating model and two stage candidates re-ranking model. Optimized F1-score 18\%.
\end{itemize}

\section{\faSitemap\ Intern Experience}

\datedsubsection{\textbf{DiDi Research Institute}}{Jul. 2016 -- Sep. 2016}
\begin{itemize}
  \item Developed taxi dispatching system which used to balance the supply and demand between urban areas.
  \item Reconstructed the log system of dispatching based on Kafka and MySQL.
\end{itemize}

\datedsubsection{\textbf{Baidu Online Network Technology(Beijing) Co.,Ltd}}{Dec. 2013 -- May. 2014}
\begin{itemize}
  \item Completed the multi-threaded development of LiveWDBBroom, improved the efficiency by two times.
  \item Completed the development of the Problems-Tracing Platform which was put into service.
  \item Passed the examination of Code Master(C++), certified as Good Coder.
\end{itemize}

\section{\faTrophy\ Academic Competitions}
\datedline{\textit{\nth{1} Place}~~Awarded in China Telecom Big Data Application Contest}{Mar. 2016}
\datedline{\textit{\nth{1} Place}~~Awarded in SIGHAN-2015 Chinese Spelling Check Task}{Jun. 2015}
\datedline{\textit{\nth{1} Place}~~Awarded in China College Students Computer Games Competition}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in China College Students Computer Application Contest}{Nov. 2013}
\datedline{\textit{\nth{1} Prize}~~Awarded in "LanQiao Cup" Software Development Contest(Beijing Division)}{Apr. 2012}
\datedline{\textit{Silver Medal~(\nth{17} / 200)}~~Awarded in ACM-ICPC Asia Beijing Regional Contest}{Nov. 2015}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Skilled in C++, Scala, Shell. Familiar with data structures and algorithms and had good programming style.
  \item Experienced in development of distributed machine learning algorithms.
  \item Strong theoretic knowledge on data mining and machine learning.
\end{itemize}



\pagebreak

\end{document}
